\textsf{Are large language models superhuman chemists?}

### 2024-10-29 src/tex/appendix.tex
recompile

\subsection{Related work}
Existing benchmarks such as those from \textcite{guo2023large}, \textcite{sun2023scieval}, \textcite{Schulze_Balhorn_2024}, \textcite{Cai_2024} fail to comply with most of the requirements stipulated above.
While these benchmarks could provide valuable insights in the short term, they cannot follow the rapid additions to the \gls{llm} space.
\chembench aims to correct this through a set of developments: compatibility with BigBench, end-to-end automation, a particular focus on chemical safety, employment of diverse prompting strategies, and specialized notation for molecules and mathematical symbols.
Moreover, our robust framework, including the platform \url{chembench.org}, will engage the community in open-source contributions.

>>>>

\subsection{Related work}
Existing benchmarks such as those from \textcite{guo2023large}, \textcite{sun2023scieval}, \textcite{Schulze_Balhorn_2024}, \textcite{Cai_2024}, \textcite{rein2023gpqagraduatelevelgoogleproofqa} fail to comply with most of the requirements stipulated above.
While these benchmarks could provide valuable insights in the short term, they cannot follow the rapid additions to the \gls{llm} space.
\chembench aims to correct this through a set of developments: compatibility with BigBench, end-to-end automation, a particular focus on chemical safety, employment of diverse prompting strategies, and specialized notation for molecules and mathematical symbols.
Moreover, our robust framework, including the platform \url{chembench.org}, will engage the community in open-source contributions.

### 2024-10-29 src/tex/ms.tex
recompile

We curated more than 2,800 question-answer pairs, evaluated leading open- and closed-source LLMs, and found that the best models outperformed the best human chemists in our study on average.
However, the models struggle with some tasks that are easy for human experts and provide overconfident predictions.

@@

\begin{table}[!h]
    \centering
    \caption{\textbf{Overview of sources of the curated questions}. The table provides an overview of the types of sources the questions have been curated from. Detailed sources are available in the source data on GitHub. Questions without source have been curated completely from scratch. Questions based on lecture notes or URL have been curated based on content presented in those resources. All questions have been rephrased, annotated, and reviewed before being added to the corpus. Note that the chemical preference questions are the main corpus of the semi-automatically generated group with \variable{output/question_count_per_dir/json_file_counts_preference.txt} questions of the total \variable{output/automatically_generated.txt}.}
    \variable{output/sources_table.tex}
    \label{tab:sources}
\end{table}

>>>>

We curated more than 2,700 question-answer pairs, evaluated leading open- and closed-source LLMs, and found that the best models outperformed the best human chemists in our study on average.
However, the models struggle with some tasks that are easy for human experts and provide overconfident predictions.

@@

\begin{table}[!h]
    \centering
    \caption{\textbf{Overview of sources of the curated questions}. The table provides an overview of the types of sources the questions have been curated from. Detailed sources are available in the source data on GitHub. Questions without source have been curated completely from scratch. Questions based on lecture notes or URL have been curated based on content presented in those resources. All questions have been rephrased, annotated, and reviewed before being added to the corpus. }
    %Note that the chemical preference questions are the main corpus of the semi-automatically generated group with \variable{output/question_count_per_dir/json_file_counts_preference.txt} questions of the total \variable{output/automatically_generated.txt}.
    \variable{output/sources_table.tex}
    \label{tab:sources}
\end{table}
